Title

### 2024-09-18 Quarto Template.qmd
Update Quarto Template.qmd

---
title: "Title"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
    theme:
      light: flatly
      dark: darkly
bibliography: /home/tim/Documents/Miscellaneous/zotero.bib
csl: /home/tim/GitHub/styles/american-medical-association.csl
editor: source
---

>>>>

---
title: "Title"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
    theme:
      light: flatly
      dark: darkly
bibliography: /Users/timvigers/Documents/Miscellaneous/zotero.bib
csl: /Users/timvigers/GitHub/styles/american-medical-association.csl
editor: source
---
